---
title: "Homework 2"
author: Megan Marziali
output: github_document
---

This document contains my solutions to homework 2 for p8105.

```{r setup}
library(tidyverse)
library(readxl)
```

# Problem 1

## Read and clean Mr. Trash Wheel

The following code imports the Mr. Trash Wheel data and cleans the data.

```{r}
trash_wheel = 
  read_xlsx("./problem_1/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
            sheet = "Mr. Trash Wheel",
            range = "A2:N408",
            na = "") %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(sports_balls_int = 
           (round(sports_balls) %>% 
           as.integer()))
```

## Read and clean precipiation data

The code below reads in and cleans precipitation data.

```{r}
precip_2017 = 
  readxl::read_excel("./problem_1/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
                     sheet = "2017 Precipitation",
                     range = "A2:B14"
                     ) %>% 
  janitor::clean_names() %>% 
  mutate(year = "2017") %>% 
  drop_na(month) %>% 
  relocate(year)

precip_2018 = 
  readxl::read_excel("./problem_1/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
                     sheet = "2018 Precipitation",
                     range = "A2:B14"
                     ) %>% 
  janitor::clean_names() %>% 
  mutate(year = "2018") %>% 
  drop_na(month) %>% 
  relocate(year)
```

Joining data and converting month to a character variable.

```{r}
month_df = 
  tibble(
    month = 1:12,
    month_name = month.name)

precip_df = 
   bind_rows(precip_2018, precip_2017)

left_join(precip_df, month_df, by = "month")
```

This dataset contains information from the Mr. Trash Wheel trash collector in Balitmore, Maryland. As trash enters the inner harbour, the trash wheel collects that trash and stores it in a dumpster. The dataset contains information on year, month and trash collected, including some specific types of trash. There are a total of `r nrow(trash_wheel)` observations in our final dataset. Additional information is included on precipitation data.

Within the precipitation dataset, there are `r nrow(precip_2017)` observations from 2017 and `r nrow(precip_2018)` from 2018. The total amount of precipitation in 2017 amounted to `r sum(precip_2017$total)` inches, and `r sum(precip_2018$total)` inches in 2018. The mean and median for precipitation in 2017 was `r round(mean(precip_2017$total), 2)` (SD: `r round(sd(precip_2017$total), 2)`) and `r round(median(precip_2017$total), 2)` (IQR: `r round(IQR(precip_2017$total), 2)`), respectively; with 2018, the mean precipitation was `r round(mean(precip_2018$total), 2)` (SD: `r round(sd(precip_2018$total), 2)`) and median precipitation was `r round(median(precip_2017$total), 2)` (IQR: `r round(IQR(precip_2017$total), 2)`).

# Problem 2





